Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2025-01-11 paper/main.tex
shrink vspace in author affiliations to fit keywords on first page

\author{Paxton C. Fitzpatrick\textsuperscript{1},
Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
Jeremy.R.Manning@Dartmouth.edu}}

>>>>

\author{Paxton C. Fitzpatrick\textsuperscript{1}, Andrew C.
Heusser\textsuperscript{1, 2}, and Jeremy R. Manning\textsuperscript{1, *}\\
\vspace{-0.5em}\small{\textsuperscript{1}Department of Psychological and Brain
Sciences}\\
\small{Dartmouth College, Hanover, NH 03755, USA}\\
\vspace{-0.5em}\small{\textsuperscript{2}Akili Interactive Labs}\\
\small{Boston, MA 02110, USA}\\
\vspace{-0.5em}\small{\textsuperscript{*}Corresponding author:
Jeremy.R.Manning@Dartmouth.edu}}
